### 2018-04-29 paper/conclusion.tex
global overlay explained + other minor

\commentAL{To rewrite as real paragraphs} Future work and prospects:
\begin{itemize}
	\item More in-depth knowledge of the user's behavior would allow to predict devices connections farther in the future;
	\item Changing devices' asymmetric keys regularly would increase security.
	Updating keys is easy in \name given the RPS that propagates new information to all nodes.
	However, more reflection would be needed to avoid key updates breaking ongoing communications passing through the devices in question.

>>>>

\commentAL{To rewrite as real paragraphs} Future work and prospects:
\begin{itemize}
	\item More in-depth knowledge of the user's behavior would allow to predict devices connections farther in the future;
	\item Changing devices' asymmetric keys regularly would increase security.
	Updating keys is easy in \name given the RPS that propagates new information to all nodes.
	However, more reflection would be needed to avoid key updates breaking ongoing communications passing through the devices in question;
	\item \name is not resilient to Byzantine nodes for now: malicious users could potentially make users pick Predictive Onion Routes that pass through them with a high probability, thus allowing the attacker to learn the file sender and receiver. To circumvent this, we would need to employ a secure Random Peer Sampling \cite{Jesi_Montresor_van_Steen_2010}, and prevent devices to lie on their probability of being online.
